A Type System for Safe and Scalable Parallelism using Logical Regions

### 2012-07-11 doc/popl2013/evaluation.tex
eval

\subsubsection{Fluid Simulation}
\label{subsec:fluid}
Fluid is based on the {\tt fluidanimate} benchmark from the PARSEC 
suite\cite{bienia11benchmarking}.  Fluid simulates the flow of an incompressible fluid
using particles that move within a regular grid of cells.  To perform operations in 
parallel the array of cells is partitioned.  Unlike
Circuit, Fluid first creates regions and partitions them before
allocating cells in regions.  Another difference is that Fluid
maintains separate regions for ghost cells rather using multiple partitions of
the regions containing shared data.  Region relationships are used for remembering
which regions are required for each grid.

@@

\subsection{Checking Overhead}
\label{subsec:overhead}
Our first Legion implementation consisted of a C++ library of Legion primitives
\cite{Legion12} with no checking of region memory accesses.  
When testing applications we frequently encountered memory corruption due to
illegal region accesses caused by application bugs.
In many cases, this corruption occurred between nodes in the cluster or on 
GPUs, environments for which debugging tools are primitive at best.
%  Finding these bugs required either multiple {\tt gdb} sessions 
%for observing execution on different nodes simultaneously or using {\tt printf} for debugging on
%GPUs.  
To location the application bugs causing these illegal accesses, we initially added 
dynamic checks on  all region accesses for both CPUs and GPUs.  
Unsurprisingly, these checks added considerable runtime overhead.  
To preserve the benefit of checking every access, but eliminate the cost of dynamic checks we implemented the type, privilege, and coherence checker we have described. 
We then rewrote all of our applications in this language and used our type checker to verify them.  Once the applications type checked we were
able to safely elide all the dynamic region access checks.

>>>>

\subsubsection{Fluid Simulation}
\label{subsec:fluid}
Fluid is based on the {\tt fluidanimate} benchmark from the PARSEC 
suite\cite{bienia11benchmarking}.  Fluid simulates the flow of an incompressible fluid
using particles that move within a regular grid of cells.  To perform operations in 
parallel the array of cells is partitioned.  Unlike
Circuit, Fluid creates and partitions regions before
allocating cells in them (i.e., partition-then-allocate).  Another difference is that Fluid
maintains separate regions for ghost cells rather using multiple partitions of
the regions containing shared data.  Region relationships are used for remembering
which regions are required for each grid.

@@

\subsection{Checking Overhead}
\label{subsec:overhead}
Our first Legion implementation consisted of a C++ library of Legion primitives
\cite{Legion12} with no checking of region memory accesses.  
When testing applications we frequently encountered memory corruption due to
illegal region accesses caused by application bugs.
In many cases, this corruption occurred between nodes in the cluster or on 
GPUs, environments for which debugging tools are primitive at best.
%  Finding these bugs required either multiple {\tt gdb} sessions 
%for observing execution on different nodes simultaneously or using {\tt printf} for debugging on
%GPUs.  
To locate the application bugs causing these illegal accesses, we initially added 
dynamic checks on  all region accesses for both CPUs and GPUs.  
Unsurprisingly, these checks added considerable runtime overhead.  
To preserve the benefit of checking every access, but eliminate the cost of dynamic checks we implemented the type, privilege, and coherence checker we have described. 
We then rewrote all of our applications in this language and used our type checker to verify them.  Once the applications type checked we were
able to safely elide all the dynamic region access checks.
